Evolving New State-of-the-Art for Voronoi Diagram and Distance Transform From JFA Using AutoML

### 2020-09-18 paper/main.tex
hfill
new title? ;-)

\usepackage{diagbox} % TABLE MASTERS - section
\usepackage{tabularx, booktabs}
\newcolumntype{L}{>{\raggedright\footnotesize}m{5.75cm}}
\renewcommand{\arraystretch}{1.2}
%%%%%%%%%%%%%

@@

% https://capitalizemytitle.com/
\title{Lord Vorotron: Finding the Best JFA Variant for the Coming Winter} % $\approx$

@@

\begin{abstract}
This paper studies a practical usage of machine learning (AutoML) to automate
research towards discovering efficient Voronoi Diagram and Distance Transform
algorithms.  As the baseline we used the Jump Flooding Algorithm (JFA) - by
finding new mutations which works best for specific data, and then ensembling
them into one, we create new state-of-the-art algorithm in this field named
\textbf{\ourjfa} \hspace{0.01cm} with time complexity \textcolor{red}{$\approx$O(1)} and
work complexity \textcolor{red}{$\approx$O(N)}.
The algorithm is faster and produces more accurate approximations. It could be
extended into 3D space in a slice-by-slice manner.  We started from the
assumption that JFA has potential for improvement - some benefits can be
observed for specific data by adding random noise and adjusting the step size in
JFA.  This showed us that, AutoML could examine this space, and find the best
possible algorithm in each case.  In the further part of the work, we discuss
the results, compare the variants and ensemble for creating the final algorithm.
\end{abstract}

@@

% FIXME: na wypadek zmiany tytulu w przyszlsoci!!!!!!!!!! ;-)
This paper\footnote{the original title for this paper was ``Lord Vorotron:
Finding the Best JFA Variant for the Coming Winter''} studies a practical usage of machine learning to automate research
towards discovering efficient Distance Transform algorithms (utilizing technique known as AutoML).
Thus, by finding mutations which works best for specific data, and then ensembling them into
one, we create new state-of-the-art algorithm in this field named \uline{\ourjfa \hspace{0.01cm} with
time complexity $\approx$O(1) and work complexity $\approx$O(N).}

@@

\begin{enumerate}
	\item Presenting new state-of-the-art variants of algorithm for Voronoi
		Diagram and Distance Transform: \newline
		\textbf{\ourjfasingle} - (Multi-domain) single best variant;
		\textbf{\ourjfa} - (Specific-domain) ensemble of weak variants; and
	\item Analyzing all possible variants of JFA: comparing error and speedup
		relative to bruteforce method
%\item Proposing, for an input set of seeds in a 2D grid, the first
%parallel algorithm in GPU to compute in constant time (i.e.
%independent of the number of seeds) a highly accurate
%Voronoi diagram and distance transform.
\end{enumerate}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
                         & Small (32-128)    & Medium (256-448)   & Large (512-1536)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & JFA           & Blabla        & ?       \\
High ($\rho$=0.01-0.1)        & JFAStar           & ?        & ?       \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Found in this paper state-of-the-art for specific domains.}
\end{table}

@@

\subsubsection{Small Shape: 32x32, 64x64, 96x96, 128x128}
% FIXME: a w srodku dwie kolumny i wykresy???????????????????????????
%                   low dense         |       high dense

\longvar{Square-Special(1.44/0.96/0.17/1.63/0.86)+Noise}

\begin{figure}[H]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[height=4.5cm]{../figures/results-small-low/legend}
		\includegraphics[width=1\linewidth]{../figures/results-small-low/figure-2-loss}
		\includegraphics[width=1\linewidth]{../figures/results-small-low/figure-3-score}
		\caption{Low Density}
		\label{Fig:noise}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[height=4.5cm]{../figures/results-small-high/legend}
		\includegraphics[width=1\linewidth]{../figures/results-small-high/figure-2-loss}
		\includegraphics[width=1\linewidth]{../figures/results-small-high/figure-3-score}
		\caption{High Density}
		\label{Fig:lnoise}
	\end{minipage}
	\label{Small Shape: 32x32, 64x64, 96x96, 128x128}
\end{figure}

% \begin{figure}[H]
% 	\centering
% 	\includegraphics[width=0.5\linewidth]{../figures/results-small-low/figure-2-loss}
% 	\includegraphics[width=0.5\linewidth]{../figures/results-small-low/figure-3-score}
% 	\caption{bla bla bla}
% 	\label{fig:abstract}
% \end{figure}

>>>>

\usepackage{diagbox} % TABLE MASTERS - section
\usepackage{tabularx, booktabs}
\newcolumntype{L}{>{\raggedright\footnotesize}m{5.75cm}}
\renewcommand{\arraystretch}{1.2}
\usepackage{makecell}
%%%%%%%%%%%%%

@@

% https://capitalizemytitle.com/
%\title{Lord Vorotron: Finding the Best JFA Variant for the Coming Winter} % $\approx$
% Evolving New State-of-the-Art for Distance Transform From JFA Using AutoML
\title{Evolving New State-of-the-Art for Voronoi Diagram and Distance Transform From JFA Using AutoML}

@@

\begin{abstract}
This paper studies a practical usage of machine learning (AutoML) to automate
research towards discovering efficient Voronoi Diagram and Distance
Transform algorithms.  As the baseline we used the Jump Flooding Algorithm
(JFA) - by finding new mutations which works best for specific data, and
then ensembling them into one, we create new state-of-the-art algorithm in
this field named \textbf{\ourjfa} \hspace{0.01cm} with best-case
\textcolor{red}{$O(1)$} time complexity and \textcolor{red}{$O(N)$} work
complexity - in addition, we introduce \textbf{\ourjfasingle}, a single
variant that in most cases outperforms original JFA with proven worst-case
\textcolor{red}{$O(\log^{*}N)$} time complexity.
The algorithm is faster and produces more accurate approximations. It could be
extended into 3D space in a slice-by-slice manner.  We started from the
assumption that JFA has potential for improvement - some benefits can be
observed for specific data by adding random noise and adjusting the step size in
JFA.  This showed us that, AutoML could examine this space, and find the best
possible algorithm in each case.  In the further part of the work, we discuss
the results, compare the variants and ensemble for creating the final algorithm.
\end{abstract}

% [FIXME]
% - additionally, we present \ourjfasingle, single variant that outperforms JFA in most cases.

@@

% FIXME: na wypadek zmiany tytulu w przyszlsoci!!!!!!!!!! ;-)
This paper\footnote{the original title for this paper was ``Lord Vorotron:
Finding the Best JFA Variant for the Coming Winter''} studies a practical usage of machine learning to automate research
towards discovering efficient Distance Transform algorithms (utilizing technique known as AutoML).
Thus, by finding mutations which works best for specific data, and then ensembling them into
one, we create new state-of-the-art algorithm in this field named \uline{\ourjfa
\hspace{0.01cm} with best-case $O(1)$ time complexity and $O(N)$ work complexity.}
In addition, we introduce \uline{\ourjfasingle, a single
variant that in most cases outperforms original JFA with proven worst-case
$O(\log^{*}N)$ time complexity.}

@@

\begin{enumerate}
	\item Presenting new state-of-the-art variants of algorithm for Voronoi
		Diagram and Distance Transform: \newline
		\textbf{\ourjfasingle} - (Multi-domain) single variant;
		\textbf{\ourjfa} - (Specific-domain) ensemble of weak variants; and
	\item Analyzing all possible variants of JFA: comparing error and speedup
		relative to bruteforce method
%\item Proposing, for an input set of seeds in a 2D grid, the first
%parallel algorithm in GPU to compute in constant time (i.e.
%independent of the number of seeds) a highly accurate
%Voronoi diagram and distance transform.
\end{enumerate}

@@

\hl{powinno byc ograniczone do 3 PARAMETROW! wymyslis nowa funkcje}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagecolor{yellow}

@@

% FIXME: to nie jest wyjscie!!!
% \makecell[l]{
% 	Square-\\
% 	Special(1.44/0.96/0.17/1.63/0.86)+\\
% 	Noise}           &

\begin{table}[H] \centering
\begin{tabular}{@{}l|ccc@{}}
\toprule
\hspace*{0.175cm}\diagbox{\textbf{Density}}{\textbf{Shape}}
                         & Small (32-128)    & Medium (256-448)   & Large (512-1536)  \\
\midrule
Low ($\rho$=0.00005-0.001)    & 
	Bruteforce & 
	?          & 
	?          \\
High ($\rho$=0.01-0.1)        & 
	?          &
	?             &
	?          \\
\bottomrule
\end{tabular}
\vspace{1em}
\caption{Found in this paper state-of-the-art for specific domains.}
\end{table}

@@

\subsubsection{Small Shape: 32x32, 64x64, 96x96, 128x128}

\longvar{Square-Special(1.44/0.96/0.17/1.63/0.86)+Noise}
\newline
and\hfill \longvar{Square-Special(1.07/0.24/0.9/1.88/0.64)}

\begin{figure}[H]
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[height=4.5cm]{../figures/results-small-low/legend}
		\includegraphics[width=1\linewidth]{../figures/results-small-low/figure-2-loss}
		\includegraphics[width=1\linewidth]{../figures/results-small-low/figure-3-score}
		\caption{Low Density}
		\label{Fig:noise}
	\end{minipage}\hfill
	\begin{minipage}{0.48\textwidth}
		\centering
		\includegraphics[height=4.5cm]{../figures/results-small-high/legend}
		\includegraphics[width=1\linewidth]{../figures/results-small-high/figure-2-loss}
		\includegraphics[width=1\linewidth]{../figures/results-small-high/figure-3-score}
		\caption{High Density}
		\label{Fig:lnoise}
	\end{minipage}
\end{figure}
